An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-31 comment.tex
add abstract

\begin{abstract}
pooling is a popular strategy for increasing
SARS-CoV-2 testing throughput. One popular pooling scheme is Dorfman
pooling: test $N$ individuals simultaneously. If the test is positive, each individual is  then tested separately. When error rates are taken into consideration,
most analyses assume that including extra infected samples in a pooled test has no effect 
on the pooled test outcome. We refute this assumption with experimental data
and suggest a novel probabilistic model for the outcomes of pooled tests. Our model is
parsimonous and assumes as little as possible. We analyze the false-negative
rate (i.e., the probability of a negative result for an infected individual) of
Dorfman pooling via a our model. We show that one can expect a 60-80\% increase in
false-negative rates under Dorfman pooling, for reasonable parameter
values. Moreover, we show that the false-negative rates under Dorfman
pooling increase when the prevalence of infection decreases.
In most pooling schemes, identifying an infected
individual requires positive results in multiple tests and hence
substantially increases false-negative rates. Furthermore, this
phenomenon is more pronounced when infection prevalence is low ---
exactly when pooling is most efficient. Thus, pooling presents an
inherent trade-off: it is most efficient when it is least
accurate. The deterioration of false-negative rates and the
aforementioned trade-off are inherent problems of pooling schemes and
should be kept in mind by practitioners and policy makers.
\end{abstract}
\newpage

>>>>

\begin{abstract}
pooling is a popular strategy for increasing SARS-CoV-2 testing
throughput. One popular pooling scheme is Dorfman pooling: test $N$
individuals simultaneously. If the test is positive, each individual
is then tested separately. Most analyses of pooling scheme error rates
assume that including extra infected samples in a pooled test has no
effect on the pooled test outcome. We refute this assumption with
experimental data and suggest a novel and parsimonous probabilistic
model for the outcomes of pooled tests. As an application, we analyze
the false-negative rate (i.e., the probability of a negative result
for an infected individual) of Dorfman pooling via a our model. We
show that the false-negative rates under Dorfman pooling increase when
the prevalence of infection decreases. Thus, pooling is riskiest
exactly when it is most efficient. Conclusion/ summary.
%% This is an inherent problem of Dorfman pooling and should be kept in
%% mind by practitioners and policy makers alike.
\end{abstract}
\newpage
